The Hosting Environment of the Advanced Resource Connector middleware

### 2008-10-01 doc/hed/ARCHED_article.tex
Removed "crap" and fixed bibliography

\documentclass{book}
%\documentclass{article}                            %for shorter notes
\usepackage{graphicx}                              %for PNG images (pdflatex)
%\usepackage{graphics}                              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
\usepackage{ifthen}
\newboolean{brieftechdesc}
\newboolean{verbtechdesc}
\setboolean{brieftechdesc}{false}
\setboolean{verbtechdesc}{true}
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {J. J\"{o}nemo, Aleksandr Konstantinov},
  pdftitle = {The Hosting Environment of the Advanced Resource Connector middleware},
  pdfsubject = {Paper subject},
  pdfkeywords = {HED,ARC},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

\vspace*{1.5cm}
%%%%---- A list of authors ----
    {\centering \large J. J\"{o}nemo\footnote{johan.jonemo@hep.lu.se}, Aleksandr Konstantinov\footnote{aleksandr.konstantinov@fys.uio.no} \large \par}

@@

The HED is a relatively young framework and there are quite a few rough edges and non-flexible solutions. The situation will hopefully improve with time. We would be grateful for any suggestions how to improve the architecture and the code of the HED. Statements like "you are doing crap, I shall use Axis instead" are understood but not welcome and are usually reacted adequately.

>>>>

\documentclass{book}
%\documentclass{article}                            %for shorter notes
\usepackage{graphicx}                              %for PNG images (pdflatex)
%\usepackage{graphics}                              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
\usepackage{ifthen}
\newboolean{brieftechdesc}
\newboolean{verbtechdesc}
\setboolean{brieftechdesc}{false}
\setboolean{verbtechdesc}{true}
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {J. J\"{o}nemo, A. Konstantinov},
  pdftitle = {The Hosting Environment of the Advanced Resource Connector middleware},
  pdfsubject = {Paper subject},
  pdfkeywords = {HED,ARC},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

\vspace*{1.5cm}
%%%%---- A list of authors ----
    {\centering \large J. J\"{o}nemo\footnote{johan.jonemo@hep.lu.se}, A. Konstantinov\footnote{aleksandr.konstantinov@fys.uio.no} \large \par}

@@

The HED is a relatively young framework and there are quite a few rough edges and non-flexible solutions. The situation will hopefully improve with time. We would be grateful for any suggestions how to improve the architecture and the code of the HED. 
%Statements like "you are doing crap, I shall use Axis instead" are understood but not welcome and are usually reacted adequately.
